### 2020-06-28 manuscript/report_appendix.Rmd
minor fixes

(ref:tab-example-trans) Transition probabability estimates for example data from Andersson et al. (2017)

@@

(ref:tab-example-resp) Response parameter estimates for example data from Andersson et al. (2017)

>>>>

(ref:tab-example-trans) Transition Probabability Estimates for Example Data from Andersson et al. (2017)

@@

(ref:tab-example-resp) Response Parameter Estimates for Example Data from Andersson et al. (2017)
